Contracts for Contracts

### 2023-07-10 paper/introduction.tex
misc

%Apart from the investigating effort to certify and verify smart contract
%programs, language designers are responsible to empower programmers with better
%linguistic solutions to secure smart contracts in the first place.
To address these issues, we argue that \emph{behavioral software
contracts}~\cite{DBLP:conf/tools/Meyer98a} should play a fundamental role in
the development of \emph{smart contract} programs.
Similar to smart contracts, behavioral contracts is an agreement, too. They
specify assumptions and guarantees between software components, just as
smart contracts specify assumptions and guarantees between economic parties.
The specified assumptions and guarantees are executable specifications
written in the same programming language syntax, and will be monitored and
reported if violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
design-by-contract methodology \cite{DBLP:conf/tools/Meyer98a,
DBLP:books/ph/Meyer97}, various styles of behavioral contracts have been
adopted in Java, Haskell, C\#, Python, Racket, Elixir
\cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \note{cite}
Studies \cite{DBLP:conf/rodin/Chalin06, DBLP:books/ph/Meyer97}
have shown that behavioral contracts can effectively support design, development,
testing, and debugging of software systems.

>>>>

%Apart from the investigating effort to certify and verify smart contract
%programs, language designers are responsible to empower programmers with better
%linguistic solutions to secure smart contracts in the first place.
To address these issues, we argue that \emph{behavioral software
contracts}~\cite{DBLP:conf/tools/Meyer98a} should play a fundamental role in
the development of \emph{smart contract} programs.
Similar to smart contracts, behavioral contracts is an agreement, too. They
specify assumptions and guarantees between software components, just as
smart contracts specify assumptions and guarantees between economic parties.

Behavioral contracts are appealing to programmers since the specified
assumptions and guarantees are executable specifications written in the same
programming language syntax, and will be monitored and reported if violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
design-by-contract methodology \cite{DBLP:conf/tools/Meyer98a,
DBLP:books/ph/Meyer97}, various styles of behavioral contracts have been
adopted in Java, Haskell, C\#, Python, Racket, Elixir
\cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \note{cite}
Studies \cite{DBLP:conf/rodin/Chalin06, DBLP:books/ph/Meyer97}
have shown that behavioral contracts can effectively support design, development,
testing, and debugging of software systems.
